Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\subsection{Experiment Result}
The following tables describe a summary of the experiment results that have been performed with three different alpha values. The result is on all test cases, IS2 cases to IS4 cases were successfully detected by regression and critical path analysis is appropriate. It's just that for the SI1 case, only the alpha value is 0.1
which can successfully detect the regression and determine the source of the cause of the regression with critical path analysis. Other alpha values cannot detect regression and do not perform critical path analysis.

>>>>

\subsection{Experiment Result}
The following tables \ref{test-1} \ref{test-2} \ref{test-3} describe a summary of the experiment results that have been performed with three different alpha values. The result is on all test cases, IS2 cases to IS4 cases were successfully detected by regression and critical path analysis is appropriate. It's just that for the SI1 case, only the alpha value is 0.1
which can successfully detect the regression and determine the source of the cause of the regression with critical path analysis. Other alpha values cannot detect regression and do not perform critical path analysis.
